%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ethan Yang} \\ \vspace{1pt}
    \small 647-336-9608 $|$ \href{mailto:ethn.yang@mail.utoronto.ca}{\underline{ethn.yang@mail.utoronto.ca}} $|$ 
    \href{https://linkedin.com/in/ey6}{\underline{linkedin.com/in/ey6}} $|$
    \href{https://github.com/e-yang6}{\underline{github.com/e-yang6}} $|$
    \href{https://ethanyang.dev/}{\underline{ethanyang.dev}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Toronto}{Toronto, ON}
    {Bachelor of Applied Science in Electrical \& Computer Engineering + \textbf{PEY Co-op}}{Sep. 2025 -- May 2030}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: C/C++, Python, Java, JavaScript, TypeScript, HTML/CSS, MATLAB} \\
    \textbf{Frameworks}{: React, Node.js, Flask} \\
    \textbf{Developer Tools}{: Git, VS Code, Visual Studio, PyCharm, Eclipse, Arduino} \\
    \textbf{Libraries}{: Matplotlib, OpenCV}
  }}
\end{itemize}


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{QuantiFi (3rd Place, UTEFA QuantiFi Competition 2025)} $|$ \emph{Python}}{Nov. 2025}
      \resumeItemListStart
        \resumeItem{Developed a quantitative trading strategy for an algorithmic trading competition using Python}
        \resumeItem{Backtested trading models on historical data to evaluate performance}
        \resumeItem{Applied parameter optimization and risk analysis to improve strategy returns}
  \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Stop! Don’t Go On (Finalist, GoOnHacks 2025)} $|$ \emph{React, Python, Flask, OpenCV, Arduino}}{Nov. 2025}
      \resumeItemListStart
        \resumeItem{Built a computer vision application to detect unproductive behavior and trigger automated alerts}
        \resumeItem{Integrated real-time face tracking using OpenCV with hardware control via Arduino}
        \resumeItem{Designed and served REST APIs using Flask to support frontend interactions}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{binder.} $|$ \emph{React, TypeScript, Node.js}}{Oct. 2025}
  \resumeItemListStart
    \resumeItem{Built a swipe-style marketplace application for browsing secondhand deals with AI-assisted price recommendations}
    \resumeItem{Implemented real-time web scraping of Kijiji listings with background processing}
    \resumeItem{Integrated AI-powered negotiation coaching and price analysis features}
    \resumeItem{Designed dynamic UI interactions using React and TypeScript for responsive cross-platform use}
  \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Monte Carlo Simulation} $|$ \emph{C++, Python, Matplotlib}}{Oct. 2025}
      \resumeItemListStart
        \resumeItem{Implemented a Monte Carlo simulation in C++ to model stock price evolution using Geometric Brownian Motion}
        \resumeItem{Generated and visualized simulated price paths and distributions using Matplotlib}
        \resumeItem{Computed statistical metrics including mean and variance from simulation results}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Volleyball Coach}{Sep. 2021 -- Present}
    {Toronto Thunderbolts Volleyball Club}{Markham, ON}
    \resumeItemListStart
      \resumeItem{Led and organized training sessions for youth athletes}
      \resumeItem{Provided technical instruction and performance feedback}
      \resumeItem{Collaborated with coaching staff to plan practices and tournaments}
    \resumeItemListEnd

  \resumeSubheading
    {Barista}{July 2025 -- Aug. 2025}
    {Cotti Coffee}{Markham, ON}
    \resumeItemListStart
      \resumeItem{Delivered customer service in a fast-paced environment}
      \resumeItem{Handled point-of-sale transactions accurately}
      \resumeItem{Maintained cleanliness and operational standards}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
