%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ethan Yang} & Email : \href{mailto:ethn.yang@mail.utoronto.ca}{ethn.yang@mail.utoronto.ca} \\
  \href{https://www.linkedin.com/in/ey6/}{linkedin.com/in/ey6} \enspace\textbar\enspace \href{https://github.com/e-yang6}{github.com/e-yang6} & Mobile : +1-647-336-9608 \\
\end{tabular*}

\vspace{4pt}
\noindent Seeking a software/quantitative engineering internship to apply strong C++/Python, mathematical modelling, and problem-solving skills to high-performance, data-driven systems.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Toronto}{Toronto, ON}
      {Bachelor of Applied Science in Computer Engineering (Expected 2030)}{Sept. 2025 -- Present}

    \resumeSubheading
      {SHAD Program -- University of Prince Edward Island}{Charlottetown, PEI}
      {\upshape Selective national enrichment program in STEM, innovation, entrepreneurship, and leadership}{July 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cotti Coffee}{Toronto, ON}
      {Barista}{July 2025 -- Aug. 2025}
      \resumeItemListStart
        \item\small{Delivered high-quality service in a fast-paced environment while managing multiple simultaneous orders.}
        \item\small{Improved workflow efficiency by streamlining preparation sequences and minimizing downtime.}
      \resumeItemListEnd

    \resumeSubheading
      {Toronto Thunderbolts Volleyball Club}{Toronto, ON}
      {Volleyball Coach}{Sept. 2024 -- Aug. 2025}
      \resumeItemListStart
        \item\small{Planned and led structured training sessions, mentoring athletes aged 7--14 to improve performance.}
        \item\small{Developed game strategies and promoted communication, teamwork, and discipline.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubItem{\href{https://github.com/e-yang6/MonteCarloSimulation}{Stock Price Simulation and Risk Analysis}}
      {Developed a C++/Python model using geometric Brownian motion and Monte Carlo simulations (10k+ paths) to analyze price dynamics and risk; visualized outcomes with Matplotlib.}

    \resumeSubItem{\href{https://github.com/e-yang6/BondPricer}{Bond Pricer}}
      {Implemented a C++ fixed-income pricing engine with support for coupons, YTM, duration, and convexity; validated results using numerical methods and test cases.}

  \resumeSubHeadingListEnd

%-----------ACTIVITIES & LEADERSHIP------------
\section{Activities \& Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Robotics for Space Exploration (RSX), University of Toronto}{Toronto, ON}
      {Software Developer}{Sept. 2025 -- Present}
      \resumeItemListStart
        \item\small{Developing robotic control software using Python, C++, and ROS for autonomous space systems.}
      \resumeItemListEnd

    \resumeSubheading
      {Music Council -- Milliken Mills High School}{Markham, ON}
      {President}{June 2024 -- June 2025}
      \resumeItemListStart
        \item\small{Led a 25-member executive team to organize concerts and school-wide events, raising over \$10k for the school's music department.}
      \resumeItemListEnd

    \resumeSubheading
      {DECA -- Milliken Mills High School}{Markham, ON}
      {Trainer}{June 2024 -- June 2025}
      \resumeItemListStart
        \item\small{Coached members in business case analysis and presentation, contributing to provincial qualifications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS & ADDITIONAL INFORMATION------------
\section{Skills \& Additional Information}
 \resumeSubHeadingListStart
   \resumeItem{Programming Languages}{C++, Python, Java, JavaScript, HTML, CSS}
   \resumeItem{Libraries \& Tools}{NumPy, Matplotlib, Git, ROS}
   \resumeItem{Relevant Coursework (planned/ongoing)}
     {Data Structures \& Algorithms, Discrete Mathematics, Linear Algebra, Probability \& Statistics, Digital Systems, Object-Oriented Programming}
   \resumeItem{Honours}{Canadian Senior Mathematics Contest \& Canadian Computing Contest Distinction (Top 25\% in Canada), Waterloo Pascal Math Contest Honour Roll \& Medalist (Top 115 in Canada), DECA ICDC Qualifier, National Volleyball Silver Medalist (15U), UofT Engineering Entrance Scholarship, IB Diploma}
   \resumeItem{Languages}{English (Fluent), Mandarin (Full Professional Fluency)}
   \resumeItem{Interests}{Algorithmic trading, financial markets, global macroeconomics, competitive volleyball, music production, robotics, behavioral strategy}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
