%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{\href{https://github.com/e-yang6/stop-dont-go-on/tree/finished}{Stop! Don't Go On!}} $|$ \emph{React, TypeScript, Python, Flask, OpenCV}}{Oct 2025}
    \resumeItemListStart
        \resumeItem{GoOnHacks 2025 finalist}
        \resumeItem{Developed a computer vision accountability app that detects bad habits and intervenes with screen alerts, countdown timers, and math challenges.}
        \resumeItem{Integrated optional Arduino hardware with servo-controlled camera tracking and water spray deterrent for physical feedback.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://github.com/e-yang6/binder}{binder.}} $|$ \emph{TypeScript, React, Tailwind CSS, Python, Gemini API}}{Oct 2025}
    \resumeItemListStart
        \resumeItem{Created a Tinder-inspired marketplace browser for Kijiji with a swipe-based React interface and real-time listing updates.}
        \resumeItem{Integrated a Python scraper for dynamic data collection and leveraged the Gemini API for AI-powered price evaluation.}
        \resumeItem{Built responsive, maintainable UI components and managed application state efficiently using TypeScript and Tailwind CSS.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://github.com/e-yang6/MonteCarloSimulation}{Stock Price Simulation and Risk Analysis}} $|$ \emph{C++, Python, NumPy, Matplotlib}}{Sep 2025}
    \resumeItemListStart
        \resumeItem{Built Monte Carlo simulations to model Geometric Brownian Motion and forecast stock price paths.}
        \resumeItem{Visualized simulation outputs and return distributions using Python libraries for analysis and reporting.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
